Preserving Reciprocal Consistency in Distributed Graph Databases

### 2020-02-25 paper/main.tex
dockerise delta

The \emph{Delta} protocol is designed to prevent the occurrence of dirty writes to maintain structural integrity of the graph. A client-server model is assumed, with transactions comprised of a graph traversal (set of read operations) followed by a series of writes. There are two distinct phases, in the first phase transactions attempt perform reads and write provisionally. If successful an atomic commitment protocol is invoked, else the transaction is aborted and tentative writes are removed.

@@

The \emph{Delta} protocol influences the rate of corruption reducing the probability a transaction corrupts an edge, $q^{new}_i$. To simplify the derivation of the new conflict probability it was assumed. This leaves the Figure 6 as the only source of corruption. From this the following probability can be formulated:
$$ q^{new}_i = P \left[ ( T_x >  \Delta + X) \cap (T_y > \Delta-X) \right]$$
The arrival times of $T_x,T_y$ are assumed exponentially distributed , $X \sim \exp (\frac{\lambda P_i}{2N_i})$. The transmission times $M_1, M_2 \sim \exp (\delta)$ and are \emph{iid}. The complete derivation of $q_i$ is provided in Appendix A.

@@

The graph consisted of five edge types, $N_1=10^4, N_2=10^5, N_3=10^6, N_4=10^7, N_5=10^8$ with access probabilities $p_1 =0.5, p_2 =0.26, p_3=0.13, p_4=0.07$ and $p_5 =0.04$. The number of read operations per query is distributed geometrically starting at $2$, with an average of $15$. In all edge types, a fraction $0.3$ are distributed, the remainder are local. The database is initial clean and considered to be corrupted when $10$\% ($\gamma = 0.1$) of all edges are corrupted. The time taken under operational corruption $U$, is measured in hours. $U$ considered for a range of transaction arrival rates, $\lambda = (100, ..., 1000)$.

@@

TODO: add aborts/s
TODO: discuss results

>>>>

The \emph{Delta} protocol is designed to prevent the occurrence of dirty writes to maintain structural integrity of the graph. A client-server model is assumed, with transactions comprised of a graph traversal (set of read operations) followed by a series of writes - for simplicity a single write is assumed. There are two distinct phases, in the first phase transactions attempt perform reads and write provisionally. If successful an atomic commitment protocol is invoked, else the transaction is aborted and tentative writes are removed.

@@

The \emph{Delta} protocol influences the rate of corruption reducing the probability a transaction corrupts an edge, $q^{new}_i$. To simplify the derivation of the new conflict probability it was assumed. This leaves the Figure 6 as the only source of corruption. From this the following probability can be formulated:
$$ q^{new}_i = P \left[ ( T_x >  \Delta + X) \cap (T_y > \Delta-X) \right]$$
The arrival times of $T_x,T_y$ are assumed exponentially distributed , $X \sim \exp (\frac{\lambda P_i}{2N_i})$. The transmission times $M_1, M_2 \sim \exp (\delta)$ and are \emph{iid}. The complete derivation of $q^{new}_i$ is provided in Appendix A.

@@

The graph consisted of five edge types, $N_1=10^4, N_2=10^5, N_3=10^6, N_4=10^7, N_5=10^8$ with access probabilities $p_1 =0.5, p_2 =0.26, p_3=0.13, p_4=0.07$ and $p_5 =0.04$. The number of read operations per query is distributed geometrically starting at $2$, with an average of $15$. In all edge types, a fraction $0.3$ are distributed, the remainder are local. The database is initial clean and considered to be corrupted when $10$\% ($\gamma = 0.1$) of all edges are corrupted. The time taken under operational corruption $U$, is measured in hours. $U$ considered for a range of transaction arrival rates, $\lambda = (100, ..., 2000)$.

@@

TODO: add aborts/s \\
TODO: discuss results
